### 2022-06-23 manuscript.tex
Merge pull request #243 from SORTEE-Github-Hackathon/RCO-saeed-cover-letter [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/28647d1b51aa7df9b1214fa3fc7d0743b00d665e.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/28647d1b51aa7df9b1214fa3fc7d0743b00d665e/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2551271965

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/dc28d7dd993d0f5ca61b1bd7fc59d1cc22e39ce2/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/dc28d7dd993d0f5ca61b1bd7fc59d1cc22e39ce2}{SORTEE-Github-Hackathon/manuscript@dc28d7d}
on June 23, 2022.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/28647d1b51aa7df9b1214fa3fc7d0743b00d665e/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/28647d1b51aa7df9b1214fa3fc7d0743b00d665e}{SORTEE-Github-Hackathon/manuscript@28647d1}
on June 23, 2022.
